%-------------------------
% Resume in Latex
% Author : Guilherme Nascimento
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://vilih.com/}{\Large Guilherme Nascimento}} & Email : \href{mailto:gnlnascimento@gmail.com}{gnlnascimento@gmail.com}\\
  \href{http://vilih.com/}{http://www.vilih.com} & Mobile : +55-21-98180-4006 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universidade Estácio de Sá}{Rio de Janeiro, Brazil}
      {Bachelor of Computer Science}{2023 - 2026}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {DBC Company}{Remote}
      {Software Engineer}{Present}
      \resumeItemListStart
    \resumeItem{High-Performance Systems}
      {Developed efficient systems using .NET, Dapper, and React that improved workflow efficiency by 70\%. Modernized backend services by migrating from .NET 6 to .NET 8 and React 16 to React 18, enhancing performance and scalability.}
    \resumeItem{Micro-Frontend Architecture}
      {Led the development of micro-frontends with React and TypeScript, increasing system modularity and team autonomy.}
    \resumeItem{Testing Framework}
      {Wrote automated tests using xUnit (backend) and Playwright (frontend), ensuring code stability and high test coverage.}
    \resumeItem{DevOps Infrastructure}
      {Managed and integrated CI/CD pipelines for microfrontends and RESTful APIs using Azure DevOps. Utilized monitoring solutions with Kibana and Kubernetes dashboards to track application health metrics and logs}
    \resumeItem{Backend Development}
      {Designed and managed RESTful APIs with ASP.NET Core 6/8, following architectural patterns such as clean architecture and vertical slice architecture.}
    \resumeItem{SQL Command Tool}
      {Developed an internal application for SQL command search integrated with Dapper for executing queries efficiently. Standardizing writing and execution of queries.}
  \resumeItemListEnd

   \resumeSubheading
  {DBC Company}{Remote}
  {Frontend Developer Intern}{01/2023 - 04/2023}
  \resumeItemListStart
    \resumeItem{Recruitment Portal}
      {Developed a new candidate portal workflow using React, TypeScript and RTK Query, improving communication between candidates and the company. The unified system consistently handled over 1,000 registrations per enrollment period.}
    \resumeItem{Integration System}
      {Optimized communication and registration flows by integrating emails and Google Forms into a unified system, streamlining the candidate experience and improving data collection efficiency.}
    \resumeItem{Testing Implementation}
      {Implemented frontend tests using React Testing Library and Vitest, ensuring application reliability and functionality across different user scenarios.}
    \resumeItem{Responsive Web Design}
      {Developed and maintained responsive web applications with React and TypeScript, implementing state management solutions including Redux Toolkit and Context API.}
    \resumeItem{UI/UX Enhancement}
      {Applied UI/UX best practices to design intuitive interfaces, enhancing user experience and satisfaction through thoughtful layout, navigation, and interaction patterns.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Vili's Vault Blog \href{http://vilih.com/}{(vilih.com)}}
      {Personal technical blog designed and developed using Astro and TypeScript with Markdown-to-HTML conversion. Regularly publish content about emerging technologies, work-related topics, and personal projects.}
    \resumeSubItem{Convert Ease \href{https://convert-ease-sigma.vercel.app/}{(convert-ease-sigma.vercel.app)}}
      {High-performance web application for media format conversion built with Next.js 14, TypeScript, and Zustand for state management. Utilized FFMPEG WASM for client-side media processing and Tailwind CSS for interface design.}
  \resumeSubHeadingListEnd
%
%--------PROGRAMMING SKILLS------------
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
  \item{
    \textbf{Languages:} C\#, TypeScript, JavaScript, SQL.
  }
  \item{
    \textbf{Frameworks \& Libraries:} ASP.NET Core, Entity Framework Core, React, Redux Toolkit, Tanstack Query, xUnit, Playwright, Vitest.
  }
  \item{
    \textbf{Tools \& Platforms:} Docker, Azure DevOps, CI/CD Pipelines, Kubernetes, Kibana, Git.
  }
  \item{
    \textbf{Databases \& ORMs:} SQL Server, Dapper, Entity Framework Core.
  }
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
